---
title: "P8105 Homework 6"
author: "Jiayi Zhou(jz3336)"
date: "12/7/2020"
output: github_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(readxl)

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Probelm 1:

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1,
    )
  ) %>% 
  filter(city_state != "Tulsa_AL",
         victim_race %in% c("White", "Black")) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city:
```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore_MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digit = 3)
```

Try this across cities:
```{r}
model_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

Plot:
```{r}
model_results_df %>% 
  filter(term == "victim_raceWhite") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

__comment:__
This is plot of odd ratios which compared white homicide victims to black homicide victims. The odd ratios in the majority of the city sates are larger than 1. Therefore, relative to black homicide victim, homicides in which the victims are white are much more likely to be resolved.

## Problem 2

#### Clean data:
```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(case_when(
      babysex == 2 ~ "female", 
      babysex == 1 ~ "male"
    )),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
    )
```

check for NA:
```{r}
birthweight %>% 
  drop_na()
```
There is no NA since the data frame stayed the same after  `drop_na`

#### Fit Models:

I hope to build a model using family income and mother's weight gain during pregnancy as predictors while baby's birth wight is the outcome. I hypothesized that baby's birth weight is positively influenced by family income and mother's weight gain during pregnancy. Therefore, I updated my dataset and only kept the variables that I would like to investigate and needed by the other two models.
```{r}
birthweight_df =
  birthweight %>% 
  select(bwt, gaweeks, blength, bhead, babysex, fincome, wtgain)
```

my model:
```{r}
model_1 = lm(bwt ~ fincome + wtgain, data = birthweight_df) 

#check result
model_1 %>% 
  broom::tidy()
```

plot of model residuals against fitted values:
```{r}
birthweight_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() + 
  labs(
    title = "Plot of residuals vs. fitted values", 
    x = "Fitted values", 
    y = "Residuals", 
    caption = "Model 1"
  )
```

Cross validation:
```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    model_1  = map(train, ~lm(bwt ~ fincome + wtgain, data = .x)),
    model_2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3  = map(train, ~lm(bwt ~ blength*bhead*babysex, data = .x))) %>% 
  mutate(
    rmse_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))
```

plot showing the distribution of RMSE values for each candidate model:
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
    title = "Violin plot comparing RMSE value for the three candidate models", 
    x = "Model", 
    y = "RMSE"
  )
```
__comment__: 
The best model is model three which used head circumference, length, sex, and all interactions (including the three-way interaction) between these as the predictors of baby's birth weight.

## Problem 3:
Set up
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

r squared
```{r}
#Bootstrapping
r_squared = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(strap_number, results) %>% 
  unnest(results)


#Distribution plot
r_squared %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = " The distribution of r squared"
  )

#Confidence interval
r_squared %>% 
  summarize(
    CI_lower = quantile(r.squared, 0.025),
    CI_upper = quantile(r.squared, 0.975)
  )
```



log(beta0*beta1)
```{r}
beta = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(strap_number, results) %>% 
  unnest(results)  %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate) %>% 
  select(strap_number, `(Intercept)`,  tmin) %>% 
  group_by(strap_number) %>% 
  summarise_all(na.omit) %>% 
  mutate(
    logbetas = log(`(Intercept)`* tmin)
  )

##Distribution plot
beta %>% 
  ggplot(aes(x = logbetas)) +
  geom_density() +
  labs(
    title = " The distribution of log(beta0*beta1)"
  )


#Confidence interval
beta %>% 
  summarize(
    CI_lower = quantile(logbetas, 0.025),
    CI_upper = quantile(logbetas, 0.975)
  )
```

